Concurrent Programming with CXL

### 2020-06-22 book/paper.tex
Working on exercises
Latest

\section*{Exercises}
\begin{enumerate}
\item Change the code in Figure~\ref{fig:boundedbuffer} so that
\texttt{produce()} fails if the buffer is full rather than block.
\texttt{produce()} should return \texttt{False} if it fails
and return \texttt{True} if it succeeds.
\item Implement a \emph{bounded stack}.  Method \texttt{push(item)}
should block if the stack is full.  Method \texttt{pop()} should block
until the stack is non-empty and then return an item.
\item Implement a thread-safe GPU allocator.  There are \texttt{N} GPUs identified
by the numbers
1 through \texttt{N}.  Method \texttt{gpuAlloc()} returns the identifier
of an available GPU, blocking if there is currently no available GPU.
Method \texttt{gpuRelease(gpu)} releases the given GPU.  It never needs
to block.
\end{enumerate}

@@

Progress is a weak form of liveness.  It says that \emph{some}
process can enter, but it does not prevent a scenario such as
the following.  There are three processes repeatedly trying to
enter a critical section using a spinlock.  Two of
the processes successfully enter, alternating, but the third
process never gets a turn.  This is an example of
\texttt{starvation}.  With a spinlock, this scenario could
even happen with two processes.  Initially both processes
try to acquire the spinlock.  One of the processes is
successful and enters.  After the process leaves, it immediately
tries to re-enter.  This state is identical to the initial
state, and there is nothing that prevents the same process
from acquiring the lock yet again.

>>>>

\section*{Exercises}
\begin{enumerate}
\item Change the code in Figure~\ref{fig:boundedbuffer} so that
\texttt{produce()} fails if the buffer is full rather than block.
\texttt{produce()} should return \texttt{False} if it fails
and return \texttt{True} if it succeeds.
\item Implement a \emph{bounded stack}.  Method \texttt{push(item)}
should block if the stack is full.  Method \texttt{pop()} should block
until the stack is non-empty and then return an item.
\item Implement a thread-safe GPU allocator by modifying Figure~\ref{fig:gpu}.
There are \texttt{N} GPUs identified by the numbers
1 through \texttt{N}.  Method \texttt{gpuAlloc()} returns the identifier
of an available GPU, blocking if there is currently no available GPU.
Method \texttt{gpuRelease(gpu)} releases the given GPU.  It never needs
to block.
\end{enumerate}

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{code/gpu.cxl}
\end{code}
\caption{[gpu.cxl] A thread-unsafe GPU allocator.}
\label{fig:gpu}
\end{figure}

@@

Progress is a weak form of liveness.  It says that \emph{some}
process can enter, but it does not prevent a scenario such as
the following.  There are three processes repeatedly trying to
enter a critical section using a spinlock.  Two of
the processes successfully keep entering, alternating, but the third
process never gets a turn.  This is an example of
\texttt{starvation}.  With a spinlock, this scenario could
even happen with two processes.  Initially both processes
try to acquire the spinlock.  One of the processes is
successful and enters.  After the process leaves, it immediately
tries to re-enter.  This state is identical to the initial
state, and there is nothing that prevents the same process
from acquiring the lock yet again.
